-

### 2023-01-20 DRAFT_homogeneous_impact_areas.Rmd
feat: Cut out marine areas

This resolution is more that good enough for our purpose here.

@@

@@

```{r}
names(infra_agg) <- "infrastructureIndex"

infra_agg_discrete <- infra_agg %>%
  mutate(infrastructureIndex = case_when(
    infrastructureIndex < 1 ~ 0,
    infrastructureIndex < 6 ~ 1,
    infrastructureIndex < 12 ~ 2,
    infrastructureIndex >= 12 ~ 3
  ))
```

@@

```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

@@

This distribution looks reasonable. The relative propotions are similar in the fivre regions, but _Østlandet_ and _Sørlandet_ have more infrastructure in general.

>>>>

This resolution is more that good enough for our purpose here.
I see that the map extends a bit into the fjord. We want to cut away these areas. We can use a map of the outline of Norway to do this.

```{r}
outline <- st_read("data/outlineOfNorway_EPSG25833.shp")
```

The CRS needs to be identical 
```{r}
infra_trd_reclassed_agg <- st_transform(infra_trd_reclassed_agg, 25833)
```

```{r}
infra_trd_reclassed_agg_terrestrial <- st_crop(infra_trd_reclassed_agg, outline)
```

```{r, fig.cap="Infrastrcture indeks over Trondheim on a four-step discrete scale, aggregated to 1x1 km resolution using the mean function."}
tm_shape(infra_trd_reclassed_agg_terrestrial)+
  tm_raster(title="Infrastructure Index",
            style="cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="white")+
  tm_shape(outline)+
  tm_borders(lwd =2,
             col = "black")
```

I have treated the raster cells as points when cropping, so that cells where the center or the cell is outside he terrestrial delineation are removed. I think this makes the most sense for unbiased area statistics, but some coastal indicator data could also be excluded because of this. The errors would be smaller with a finer resolution raster, but computation time is a problem.

@@

### Cut out marine areas
I see that the map extends a bit into the fjord. We want to cut away these areas. We can use a map of the outline of Norway to do this.

The CRS needs to be identical 
```{r}
infra_agg <- st_transform(infra_agg, 25833)
```

```{r}
infra_agg_terrestrial <- st_crop(infra_agg, outline)
```

@@

```{r}
names(infra_agg_terrestrial) <- "infrastructureIndex"

infra_agg_discrete <- infra_agg_terrestrial %>%
  mutate(infrastructureIndex = case_when(
    infrastructureIndex < 1 ~ 0,
    infrastructureIndex < 6 ~ 1,
    infrastructureIndex < 12 ~ 2,
    infrastructureIndex >= 12 ~ 3
  ))
```

@@

<!-- Continue from here after fixing ea_spread -->
```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete)
```

@@

This distribution looks reasonable. The relative proportions are similar in the five regions, but _Østlandet_ and _Sørlandet_ have more infrastructure in general.
